Structural Divergence Analysis

### 2016-08-15 OUT/analysis-structure-CA-ANM.Rmd
cambios 15/08/2016

setwd("C:/Users/Usuario/Desktop/VariabilidadEstructuralProteica")

source("OUT/out_subset_CA/multiplot.R")
source("OUT/out_subset_CA/my-functions.R")
```

@@

# significance factors
f95 = 1.96
f99 = 2.6
f999 = 3.3
data.dir = paste("out_subset_CA", sep = "")
```

@@

>>>>

source("out_subset_CA_ANM/multiplot.R")
source("out_subset_CA_ANM/my-functions.R")
```

@@

# significance factors
f95 = 1.96
f99 = 2.6
f999 = 3.3
data.dir = paste("out_subset_CA_ANM", sep = "")
```

@@

```{r calculate MSD}
MSD.exp = mean(rowMeans(as.matrix(dri2.exp), na.rm = T), na.rm = T) 
MSD.mut = mean(rowMeans(as.matrix(dri2.mut)))
MSD.strong = mean(rowMeans(as.matrix(dri2.strong)))

df.MSD = data.frame(MSD.exp = MSD.exp, MSD.mut = MSD.mut, MSD.strong = MSD.strong)
knitr::kable(df.MSD, digits = 4)

### 2016-08-15 OUT/analysis-structure-CA-pfANM.Rmd
cambios 15/08/2016

---
title: "Structural Divergence Analysis"
author: "María Laura Marcos, Julian Echave"
date: "25 de julio de 2016"
output: html_document
---

@@

source("out_subset_CA_ANM/multiplot.R")
source("out_subset_CA_ANM/my-functions.R")
```

@@

```{r set_run_variables}
# Set options
family = "globins"
R0 = 10
enm = "ANM"

# significance factors
f95 = 1.96
f99 = 2.6
f999 = 3.3
data.dir = paste("out_subset_CA_ANM", sep = "")
```

@@

dri2.exp.fname = file.path(data.dir, paste(family, "_R0_10_beta_strong.sel_K.analysis_Keff_out_m.exp.norm.dr.squarei.csv", sep = ""))
Pn.exp.fname = file.path(data.dir, paste(family,"_R0_10_beta_strong.sel_K.analysis_Keff_out_m.exp.Pn.csv", sep = ""))
energy.exp.fname = file.path(data.dir, paste(family, "_R0_10_beta_strong.sel_K.analysis_Keff_out_m.exp.va.csv", sep = ""))

dri2.strong.fname = file.path(data.dir, paste(family, "_R0_10_beta_strong.sel_K.analysis_Keff_out_m.theo.norm.dr.squarei.csv", sep = ""))
Pn.strong.fname = file.path(data.dir, paste(family, "_R0_10_beta_strong.sel_K.analysis_Keff_out_m.theo.Pn.csv", sep = ""))
energy.strong.fname = file.path(data.dir, paste(family, "_R0_10_beta_strong.sel_K.analysis_Keff_out_m.theo.va.csv", sep = ""))

dri2.mut.fname = file.path(data.dir,paste(family, "_R0_10_beta_no.sel_K.analysis_Keff_out_m.theo.norm.dr.squarei.csv", sep = ""))
Pn.mut.fname = file.path(data.dir, paste(family, "_R0_10_beta_no.sel_K.analysis_Keff_out_m.theo.Pn.csv", sep = ""))
energy.mut.fname = file.path(data.dir, paste(family, "_R0_10_beta_no.sel_K.analysis_Keff_out_m.theo.va.csv", sep = ""))

@@

```{r set_reference_protein}
## which is the reference protein?
reference = as.character(read.table(reference.fname, header = F)[1, 1])
```

@@

## read site information of reference protein
site.info = read.csv(site.info.fname, header = T, sep = ";")

@@

```{r read_experimental_data}
# read experimental data
dri2.exp = read.csv(dri2.exp.fname, header = T)
site = site.info$site
dri2.exp = dri2.exp[, site]
rownames(dri2.exp) = protein.exp

@@

df.MSD = data.frame(MSD.exp = MSD.exp, MSD.mut = MSD.mut, MSD.strong = MSD.strong)
knitr::kable(df.MSD, digits = 4)

@@

p.facet %+% subset(d, dataset == "exp") 
p.facet %+% subset(d, dataset == "mut")
p.facet %+% subset(d, dataset == "mut+sel") 
p.facet
#p + theme(legend.position = "bottom", legend.title = element_blank())
p + theme(legend.position = "bottom")

@@

# p is just the median and quantiles
p.points.rq = ggplot(dat, aes(x = energy, y = Pn, col = dataset)) + 
    geom_point(alpha = .4, size = .2) +
    geom_line(aes(y = rq.5)) +
    geom_line(aes(y = rq.05)) +
    geom_line(aes(y = rq.95)) 
p = p.points.rq +  
    labs(x = "mode energy", y = "structural divergence") +
    coord_cartesian(xlim = c(0,2.5)) +
    scale_colour_manual(name = NULL, values = myColors) + 
    scale_fill_manual(name=NULL, values = myColors)

@@

p = ggplot(dat,aes(x=energy.mean,y=Pn.median,col=dataset,fill=dataset)) +
    geom_pointrange(aes(ymin=Pn.median.min,ymax = Pn.median.max),size=.2,alpha=.4) +
    geom_line(aes(y=rq.5))  +
    labs(x="mode energy",y="structural divergence (median Pn) ") +
    scale_colour_manual(name = NULL,values = myColors) + 
    scale_fill_manual(name=NULL,values=myColors)+
    coord_cartesian(xlim=c(0,1))

>>>>

---
title: "Structural Divergence Analysis"
author: "María Laura Marcos, Julian Echave"
date: "02 de julio de 2016"
output: html_document
---

@@

source("out_subset_CA_pfANM/multiplot.R")
source("out_subset_CA_pfANM/my-functions.R")
```

@@

```{r set_run_variables}
# Set options
family = "globins"
R0 = "NC"
enm = "pfANM"

# Significance factors
f95 = 1.96
f99 = 2.6
f999 = 3.3
data.dir = paste("out_subset_CA_pfANM", sep = "")
```

@@

dri2.exp.fname = file.path(data.dir, paste(family, "_R0_NC_beta_no.sel_K.analysis_Keff_out_m.exp.norm.dr.squarei.csv", sep = ""))
Pn.exp.fname = file.path(data.dir, paste(family,"_R0_NC_beta_no.sel_K.analysis_Keff_out_m.exp.Pn.csv", sep = ""))
energy.exp.fname = file.path(data.dir, paste(family, "_R0_NC_beta_no.sel_K.analysis_Keff_out_m.exp.va.csv", sep = ""))

dri2.strong.fname = file.path(data.dir, paste(family, "_R0_NC_beta_strong.sel_K.analysis_Keff_out_m.theo.norm.dr.squarei.csv", sep = ""))
Pn.strong.fname = file.path(data.dir, paste(family, "_R0_NC_beta_strong.sel_K.analysis_Keff_out_m.theo.Pn.csv", sep = ""))
energy.strong.fname = file.path(data.dir, paste(family, "_R0_NC_beta_strong.sel_K.analysis_Keff_out_m.theo.va.csv", sep = ""))

dri2.mut.fname = file.path(data.dir,paste(family, "_R0_NC_beta_no.sel_K.analysis_Keff_out_m.theo.norm.dr.squarei.csv", sep = ""))
Pn.mut.fname = file.path(data.dir, paste(family, "_R0_NC_beta_no.sel_K.analysis_Keff_out_m.theo.Pn.csv", sep = ""))
energy.mut.fname = file.path(data.dir, paste(family, "_R0_NC_beta_no.sel_K.analysis_Keff_out_m.theo.va.csv", sep = ""))

@@

```{r set_reference_protein}
## Which is the reference protein?
reference = as.character(read.table(reference.fname, header = F)[1, 1])
```

@@

## Read site information of reference protein
site.info = read.csv(site.info.fname, header = T, sep = ";")

@@

```{r read_experimental_data}
# Read experimental data
dri2.exp = read.csv(dri2.exp.fname, header = T)
site = site.info$site
dri2.exp = dri2.exp[, site]
rownames(dri2.exp) = protein.exp

@@

df.MSD = data.frame(MSD.exp = MSD.exp, MSD.mut = MSD.mut, MSD.strong = MSD.strong)
knitr::kable(df.MSD, digits = 4)
```

@@

p.facet %+% subset(d, dataset == "exp") 
p.facet %+% subset(d, dataset == "mut")
p.facet %+% subset(d, dataset == "mut+sel") 
p.facet

#p + theme(legend.position = "bottom", legend.title = element_blank())
p + theme(legend.position = "bottom")

@@

# p is just the median and quantiles
p.points.rq = ggplot(dat, aes(x = energy, y = Pn, col = dataset)) + 
    geom_point(alpha = .4, size = .2) +
    geom_line(aes(y = rq.5)) +
    geom_line(aes(y = rq.05)) +
    geom_line(aes(y = rq.95)) 
p = p.points.rq +  
    labs(x = "mode energy", y = "structural divergence") +
    coord_cartesian(xlim = c(0,0.5)) +
    scale_colour_manual(name = NULL, values = myColors) + 
    scale_fill_manual(name=NULL, values = myColors)

@@

p = ggplot(dat,aes(x=energy.mean,y=Pn.median,col=dataset,fill=dataset)) +
    geom_pointrange(aes(ymin=Pn.median.min,ymax = Pn.median.max),size=.2,alpha=.4) +
    geom_line(aes(y=rq.5))  +
    labs(x="mode energy",y="structural divergence (median Pn) ") +
    scale_colour_manual(name = NULL,values = myColors) + 
    scale_fill_manual(name=NULL,values=myColors)+
    coord_cartesian(xlim=c(0,0.5))

### 2016-08-15 OUT/analysis-structure-CM-ANM.Rmd
cambios 15/08/2016

source("out_subset_CA_ANM/multiplot.R")
source("out_subset_CA_ANM/my-functions.R")
```

@@

# significance factors
f95 = 1.96
f99 = 2.6
f999 = 3.3
data.dir = paste("out_subset_CA_ANM", sep = "")
```

@@

# p is just the median and quantiles
p.points.rq = ggplot(dat, aes(x = energy, y = Pn, col = dataset)) + 
    geom_point(alpha = .4, size = .2) +
    geom_line(aes(y = rq.5)) +
    geom_line(aes(y = rq.05)) +
    geom_line(aes(y = rq.95)) 
p = p.points.rq +  
    labs(x = "mode energy", y = "structural divergence") +
    coord_cartesian(xlim = c(0,2.5)) +
    scale_colour_manual(name = NULL, values = myColors) + 
    scale_fill_manual(name=NULL, values = myColors)

@@

p = ggplot(dat,aes(x=energy.mean,y=Pn.median,col=dataset,fill=dataset)) +
    geom_pointrange(aes(ymin=Pn.median.min,ymax = Pn.median.max),size=.2,alpha=.4) +
    geom_line(aes(y=rq.5))  +
    labs(x="mode energy",y="structural divergence (median Pn) ") +
    scale_colour_manual(name = NULL,values = myColors) + 
    scale_fill_manual(name=NULL,values=myColors)+
    coord_cartesian(xlim=c(0,1))

>>>>

source("out_subset_CM_ANM/multiplot.R")
source("out_subset_CM_ANM/my-functions.R")
```

@@

# significance factors
f95 = 1.96
f99 = 2.6
f999 = 3.3
data.dir = paste("out_subset_CM_ANM", sep = "")
```

@@

# p is just the median and quantiles
p.points.rq = ggplot(dat, aes(x = energy, y = Pn, col = dataset)) + 
    geom_point(alpha = .4, size = .2) +
    geom_line(aes(y = rq.5)) +
    geom_line(aes(y = rq.05)) +
    geom_line(aes(y = rq.95)) 
p = p.points.rq +  
    labs(x = "mode energy", y = "structural divergence") +
    coord_cartesian(xlim = c(0,10)) +
    scale_colour_manual(name = NULL, values = myColors) + 
    scale_fill_manual(name=NULL, values = myColors)

@@

p = ggplot(dat,aes(x=energy.mean,y=Pn.median,col=dataset,fill=dataset)) +
    geom_pointrange(aes(ymin=Pn.median.min,ymax = Pn.median.max),size=.2,alpha=.4) +
    geom_line(aes(y=rq.5))  +
    labs(x="mode energy",y="structural divergence (median Pn) ") +
    scale_colour_manual(name = NULL,values = myColors) + 
    scale_fill_manual(name=NULL,values=myColors)+
    coord_cartesian(xlim=c(0,10))

### 2016-08-15 OUT/analysis-structure-CM-pfANM.Rmd
cambios 15/08/2016

source("out_subset_CA_pfANM/multiplot.R")
source("out_subset_CA_pfANM/my-functions.R")
```

@@

# Significance factors
f95 = 1.96
f99 = 2.6
f999 = 3.3
data.dir = paste("out_subset_CA_pfANM", sep = "")
```

@@

df.MSD = data.frame(MSD.exp = MSD.exp, MSD.mut = MSD.mut, MSD.strong = MSD.strong)
knitr::kable(df.MSD, digits = 4)
```

>>>>

source("out_subset_CM_pfANM/multiplot.R")
source("out_subset_CM_pfANM/my-functions.R")
```

@@

# Significance factors
f95 = 1.96
f99 = 2.6
f999 = 3.3
data.dir = paste("out_subset_CM_pfANM", sep = "")
```

@@

df.MSD = data.frame(MSD.exp = MSD.exp, MSD.mut = MSD.mut, MSD.strong = MSD.strong)
knitr::kable(df.MSD, digits = 4)
